### 2022-07-22 paper/main.tex
more corrections on paper

\par Crime has long shaped people's lives. The fear of crime has inspired historical movements \cite{pmieszkowski} and shaped elections \cite{jliu}. While fear of crime has occurred organically throughout history, some have sought to gain politically or monetarily from a saturation of worry. One method in which this happens is through the use of media \cite{vsacco}. Through mediums such as television \cite{jshanahan} and print \cite{lheath}, researchers have long analyzed how the prevalence of crime reporting might affect consumer's perceptions of public safety.

\par While traditional media, such as television and newspapers, are frequently the subject of crime-relationship research, they have grown increasingly irrelevant. As traditional media declines \cite{rnielsen}, social media, such as Twitter, Facebook, and Reddit, has risen in its place. Due to this shift in media consumption patterns, an increasing number of people receive news through social media \cite{hkwak}, including stories that focus on crime. However, social media faces some flaws not found in the traditional media landscape. Due to the free and open nature of who can post on social media, submissions containing misinformation \cite{kognyanova} and manipulation of content \cite{aarif} have remained a challenge for social media companies to reign in.

\par As social media begins to fill traditional media's niche, one might wonder how the landscape of crime reporting and discussion might change. In this work, we analyze the discussion of crime on the social media website Reddit. Specifically, we examine how crime discussion takes shape on the 384 communities that represent the Metropolitan Statistical Areas of the United States. To measure crime discussion, we have developed a Reddit scraper to fetch submitted posts from the 384 selected communities. We then perform textual analysis techniques to identify posts that discuss crime while minimizing false positives. We analyze the data collected by the scraper to determine a community's level of crime discussion in comparison to its population, voting patterns, and documented crime rate. Lastly, we dive into the posting histories of users who post to Reddit's New York City community to identify any further trends or patterns.

@@

\subsection{Scale}

\par Before we begin the gathering of the data, we must first understand the scale at which the data should be collected. First, we are collecting data that pertains to the United States. Much research has focused on the relationship between crime and media specifically within the United States. The United States Census Bureau also provides plentiful contextual and reference data. Second, in a general sense, we want to measure at a city-level scale. The city is the base-level at which a critical mass of population can support an online community; a city provides a geographic center and a name to associate with a community. However, the definition of a city is rather murky. The definition varies on a state-by-state basis due to the nature in which a state delineates county-level subdivisions. All states are broken down into counties, but differ in how counties are partitioned. For example, New York breaks down counties into towns and cities, while North Dakota only subdivides counties into cities, with excluded areas remaining unincorporated. In this way, we can think of city limits and city populations as somewhat arbitrary. There is no consistent, uniform definition, so cities should not be compared to each other. To best equalize these differences, we use statistical area definitions provided by the United States Census Bureau.

@@

\par The Census Bureau provides several statistical area definitions to normalize city population and sizes. The first and most accurate definition is of Urban Areas (UAs) and Urban Clusters (UCs). UAs are dense clusters of people that house over 50,000 people. UCs are similarly measured dense clusters of people with between 2,500 and 50,000 residents. UAs and UCs are computed by first identifying a dense cluster of census blocks, the smallest census geography. From here, the UA or UC snakes off from the central core to include housing that fits the density requirements in less dense census blocks \cite{censusurban}. This process creates the ``true'' city limits, which are unaffected by municipal boundaries.

@@

\par When analyzing our selected Reddit communities, we need to consider the geospatial aspects of social media. In some sites, specific geographic location is intrinsic to the functionality of the product, whereas in others, anyone can browse a community for somewhere far away. For example, on Reddit there is no barrier preventing someone from, for example, Los Angeles from posting in a New York City community. Scellato et al. measure the geographic nature of social networks through the comparison of geospatial proximity of graph-connected users on four social media sites \cite{sscellato}. They found that sites, such as FourSquare, that had an explicitly geographic nature produced a higher degree of locality. However, sites that focused more on general information exchanges, such as Twitter, showed less geographic clustering.

\par The Reddit communities we are analyzing hold an interesting space between these two categories; they are both tied to place and detached from it. There is no geographic component stopping a user from posting to a distant community, but the geospatial nature of the community itself can lead to geographic clustering. In this way, we must determine if those posting in a certain community are truly local.

@@

\par An increase in a fear of crime can have implications beyond elevated negative emotions. Fear of crime has far-reaching social\cite{lheath}, political \cite{yjewkes}, and institutional \cite{vsacco} impacts. Belief in excessive amounts of crime can lead to loss of community cohesion; Heath and Gilbert found that as television news media consumption increased, distrust both in the local community and the world ``out there'' increased \cite{lheath}. Additionally, media creators often sensationalized stories, turning unfortunate incidents into grim spectacles. Those that perceived crime to be worse than others were more likely to perform excessive crime prevention actions, such as not leaving their house or engaging with the neighborhood.

\par Liu et al. describe how the prevalence of crime discussion affected the 2016 presidential election in the United States \cite{jliu}. The authors found that voters who consumed more television in turn consumed more campaign advertisements. About 15\% of campaign advertisements were about issues such as crime and violence. Frequent crime media consumers predict crime and violence issues to be worse than they really are \cite{jshanahan}. Furthermore, the authors found that excessive crime reporting and media exposure had impacts on voting patterns; those that believed crime to be worse tended to vote for more conservative candidates.

\par Worry of crime victimization can lead to the creation of institutional policies meant to combat the perceived threat. One notable example is the idea of Broken Windows Theory \cite{jwilson} and a practice that stemmed from its development, known as stop and frisk \cite{tmeares}. Broken Windows Theory states that visible signs of crime and disorder lead to further crimes and disorder \cite{jwilson}. Essentially, the theory states that ignoring minor criminal incidents can lead to more frequent and serious issues. Acting on this theory, the New York Police Department instituted a stop and frisk policy, in which police officers temporarily detained civilians suspected of carrying illegal objects \cite{tmeares}. The effectiveness of the policy, while believed to be effective at the time, has since come under scrutiny. Researchers found that only 6\% of stops resulted in arrests \cite{tmeares} and that there is no clear proof that stop and frisk contributed to the decline in crime in New York City \cite{dweisburd}. Stop and frisk was removed as a policy in 2013 when it was deemed unconstitutional \cite{tmeares}.

@@

\par While the relationship between traditional media and crime has been thoroughly researched, the relationship between social media and crime has not been as rigorously explored. Social media, which originally started as a method of connecting with friends and family, has grown and evolved beyond its humble beginnings. Social media sites, such as Twitter, are now significant sources of news for many Americans \cite{hkwak}. Walker and Masta found that nearly half of Americans consume their news from social media sites like Twitter, Facebook, and Reddit \cite{pewresearch}. This trend coincides with the decline of traditional media. Printed media, such as newspapers and magazines, as well as televised media, have consistently declined since the explosive growth of the Internet \cite{rnielsen}. Despite this, research on social media remains sparse.

Curiel et al. detail the ecosystem of crime discussion on Twitter \cite{curiel}. Specifically, they look at how often crime discussion appears in Tweets posted from users in Latin American countries. Using Twitter's geolocation tags, Tweets are subdivided down to the municipality that the original user posted from. From here, the authors compared Twitter crime discussion rates to city-level documented crime rates. They did not find a correlation between high frequencies of crime-related Tweets and high rates of reported crime. The authors conclude that the Tweets do not accurately represent actual rates of crime, but they effectively capture the worry of crime in a community.

% Paragraph about misinformation

Curiel et al. introduce an interesting observation: some of the crime-related Tweets are highly sensationalized or completely untrue \cite{curiel}. In this way, social media differs from traditional media. Traditional media acts as a gatekeeper, where only select stories and viewpoints emerge and factchecking generally exists in mainstream publications \cite{vsacco}. Social media, on the other hand, allows for a more diverse set of viewpoints and opinions. However, as moderation policies vary \cite{szannettou} on social media platforms, blatantly false stories can spread across sites if left unchecked. This proliferation of misinformation has become increasingly impactful in the United States. It has affected important events in recent American history, including presidential elections \cite{jliu} and the the response to the Covid-19 pandemic \cite{amian} \cite{ftahmsabi}. Without intervention, falsehoods and panics continue to spread across the web.

@@

\subsection{Reddit Data}
\par The Reddit dataset contains posts from the subreddits of the principal cities of the 384 MSAs of the United States as of March 2020 \cite{censusmetro}. From this list of subreddits, we scrape and store all posts that users submit. In total, 161,166 posts were gathered between April 5, 2022 and May 31, 2022. A timeline of this process can be seen in Figure \ref{fig:line-1}. The datastore archives posts in two formats. First, posts are written to a system of record to ensure that there is an authoritative data source that can be referenced. Second, pertinent information, such as post title and author, is extracted from the posts data stream and placed in a separate datastore.

@@

\par After storing data, an analysis tool runs to determine if a post is about crime. To do this, a regular expression checks if a post's title or a post's link's URL contains a crime-related keyword. These keywords were derived from actions that constitute violent crime and their synonyms, as well as generic crime-related words. In total, 124 keywords are used. If the regular expression returns a hit, a flag is raised in the database denoting that the post is about crime. Overall, 6,792 of the collected posts are estimated to discuss crime.

\par Due to the nature of text analysis, a number of false positives might be considered, while some false negatives go undetected. False negatives can be hard to detect, as they include dog-whistles, local-dependent terms, and ambiguous references \cite{curiel}. Certain posters may choose to keep their posts ambiguous so as to keep their intentions visible to only a small group \cite{aaddawood}. To determine the rate of false positives, we analyze a sample of scraped posts. We look for phrases such as ``I shot a picture'' that do not relate to crime, but contain a crime-related keyword. Of a sample of 400 posts, we find that 36 posts do not relate to crime, for an accuracy rate of 91\%. Similar analysis done on the social media site Twitter reached a rate of 66\% accuracy \cite{curiel}.

\subsection{Contextual Data}
\par A variety of data were utilized to highlight trends in the Reddit posts. One variable that subreddits are compared to is population size of the MSA. These values range from a minimum of 58,639 (Carson City, NV) and a maximum of 20,140,470 (New York-Newark-Jersey City, NY-NJ-PA). MSAs are categorized into four bins based on their size: large, medium, small, and very small. The population cutoffs are 1,000,000, 500,000, and 200,000. The large population bin contains 56 members, the medium bin contains 54 members, the small bin contains 113 members, and the very small bin contains 161 members.

\par Another variable that provides context is the political climate of an MSA. For this calculation, we consider the results of the 2020 election \cite{ap} in terms of the percent of the MSA voting Democrat. These values range from a minimum of 20.2\% (Morristown, TN) to a maximum of 80.9\% (Santa Cruz-Watsonville, CA). The MSAs are categorized into five bins based on their voting results: Very Conservative, Conservative, Moderate, Liberal, and Very Liberal. The percentage cutoffs for the bins are 37.5\%, 47.5\%, 52.5\%, and 62.5\%. The Very Conservative bin contains 112 members, the Conservative bin contains 103 members, the Moderate bin contains 57 members, the Liberal bin contains 73 members, and the Very Liberal bin contains 39 members.

\par A third variable that is considered is the documented violent crime rate of each MSA. This data is derived from the FBI's Uniform Crime Reporting \cite{ucr} statistics. \footnote{Data from the FBI mostly comes from the year that is most recent, 2019. However, not all municipalities report information, so there are slight estimations in the data \cite{ucr2}} Documented violent crime rates range from a minimum of 44.3/100,000 (Bangor, ME) to a maximum of 1,397.2/100,000 (Birmingham-Hoover, AL). We select violent crime rates for our comparison data because they are less ambiguous than property crimes. For example, police departments are less likely to differ in their definition of a homicide compared to criminal mischief. Documented crime data is also normalized using min-max normalization so that it can be compared to a similarly normalized crime discussion value from the Reddit data.

\section{Methods}
\par We use one main scraper to gather post data from Reddit. This scraper utilizes multiple different tools to gather disparate pieces of data and place them into two datastores. The scraper checks for new posts once every hour so that posts can be fetched before a user deletes them or a moderator removes them. These communities are generally slow moving, with an average of 111 posts an hour between all 384 subreddits.

\par To gather the data, the scraper first sends requests to the Reddit REST API \cite{reddit}. We use the \texttt{new} endpoint for each subreddit to check the most recent posts. The post last written to the database for each subreddit is cached in a database table so that we can take advantage of the \texttt{after} parameter of the API. This parameter allows us to take posts that have been created since a given post ID. The \texttt{after} parameter is especially useful on slower subreddits; without it, we would be fetching posts that might be months old. If the cached value does not exist or is not valid, then the most recent hundred posts are gathered. This is the maximum allowable value by the Reddit API.

\par After performing error checking to ensure all of our requests went through, each record is sent to two databases. The first is a CockroachDB database that acts as a system of record. Raw posts are stored here in a simple format: \texttt{id}, \texttt{timestamp}, and \texttt{data}, the last of which is the data retrieved from the Reddit API in JSON format. After writing to CockroachDB, the scraper then writes the JSON data from Reddit to ElasticSearch. ElasticSearch provides quick and efficient text analysis that allows for the extraction of certain keywords in post titles and URLs.

\par The scraper and databases run in Docker containers. Containerization allows the tool, as well as the databases, to run in a clean, isolated environment without worrying about being choked out by other processes. Additionally, the scraper-container is scheduled by Kubernetes to allow for a higher degree of availability and resilience. If something unexpected occurs and the tool goes down, it will simply be restarted by Kubernetes.

@@

\par In total, the Reddit scraper gathered 161,166 posts between 384 subreddits. Posts were collected between April 5th, 2022 and May 31, 2022. Table \ref{table:table-1} details the ten most active subreddits of those monitored. Similarly, Table \ref{table:table-2} lists the ten most active subreddits when normalized by population.

@@

\par Furthermore, Figure \ref{fig:map-1} displays a map of all Metropolitan Areas by the percentage of crime posts submitted to their respective subreddits. The darker the shade of green, the more posts discuss crime. The average crime discussion percentage lays at 3.5\%.

@@

\par From Figure \ref{fig:graph-1}, we can see that as population increases, documented crime rates gradually increase. This trend is semi-reflected in the crime discussion data. Crime discussion scores are roughly equivalent for the very small, small, and medium buckets. However, the large population bucket has a significantly higher crime discussion score than that of the other buckets. The large population bucket has a 6\% greater score than the medium population bucket when comparing documented crime data, but the large population bucket has a 56\% greater score than the medium population bucket when comparing crime discussion data.

\par Figure \ref{fig:cdf-1} shows a cumulative distribution function of the data by population bucket. Here, we can see that the smallest value of the class of large populations is the greatest among the four classes, while its largest value is greater than all of the other classes' largest values. This relationship remains true throughout most of the distribution, resulting in the large MSAs having the highest mean crime discussion score. When looking at the very small MSAs, we can see that some Metropolitan Areas in its category have high average crime discussion. However, a significant amount of very small MSAs have no crime discussion at all. From the CDF we can see that almost 20\% of very small MSA subreddits have not discussed crime at all. The next highest zero crime discussion class is small, with about 8\% of communities not discussing crime.

@@

\par Another factor to consider alongside crime discussion is the reported crime rate of an MSA. Higher documented crime rates can lead to increased amounts of crime discussion, as crime may affect more members of the community. To measure MSA crime rates, we use the FBI's Uniform Crime Reporting Estimates \cite{ucr}. The 384 Metropolitan Areas represent a differing level of crime rates, with a high of 1397.2 from Birmingham-Hoover, AL, a low of 44.3 from Bangor, ME, and an average of 380.9 among all MSAs. Table \ref{table:table-3} displays the MSAs with the ten highest documented crime rates. In this case, crime rates are defined as the amount of violent crime per 100,000 people. Additionally, the map in Figure \ref{fig:map-3} displays the crime rate for all Metropolitan Areas.

\begin{table}[h!]
    \centering
    \small
    \caption{Most active Metropolitan Areas per population}
    %\begin{tabu} to 1.0\textwidth {| *{3}{c|} }
    \begin{tabular}{| c | r | r |}
    \hline
    Metropolitan Statistical Area & Crime Rate & \% Crime Discussion\\ \hline
    Birmingham-Hoover, AL & 1,397.2 & 2.52 \\ \hline
    Farmington, NM & 1199.8 & 1.61 \\ \hline
    Anchorage, AK & 1194.6 & 2.36 \\ \hline
    Kansas City, MO-KS & 1159.4 & 3.16 \\ \hline
    Memphis, TN-MS-AR & 1120.5 & 3.43 \\ \hline
    Winston-Salem, NC & 1073.6 & 2.32 \\ \hline
    Albuquerque, NM & 1043.4 & 4.53 \\ \hline
    Danville, IL & 935.7 & 0.00 \\ \hline
    Pine Bluff, AR & 895.4 & 12.5 \\ \hline
    Odessa, TX & 881.8 & 4.30 \\ \hline
	\end{tabular}
	\label{table:table-4}
\end{table}

@@

\par From the data collected by our Reddit scraper, we have seen that crime discussion is widespread among the selected communities. However, while we have analyzed posts about crime, we have not yet analyzed the users that initiate this crime discussion. In doing so, we can potentially identify trends in the data that could highlight motivations behind crime posters or their submission patterns. We can also attempt to identify if crime posters are truly local by seeing if they overlap with other state and local subreddits.

@@

\par We have discussed the nature and prevalence of crime discussion on Reddit, a social media website, as it pertains to location-based communities. To obtain the necessary data and information, we have created a highly resilient Reddit scraper that fetches all posts from communities that represent the 384 Metropolitan Statistical Areas of the United States. The scraper gathered 161,166 posts over a two-month time span. Of these 161,166 posts, a total of 6,792 were determined to discuss crime.

>>>>

\par Crime has long shaped people's lives. The fear of crime has inspired historical movements \cite{pmieszkowski} and shaped elections \cite{jliu}. While fear of crime has occurred organically throughout history, some have sought to gain politically or monetarily from a saturation of worry. The calculated use of media can exacerbate this fear \cite{vsacco}. Through mediums such as television \cite{jshanahan} and print \cite{lheath}, researchers have long analyzed how the prevalence of crime reporting might affect consumer's perceptions of public safety.

\par While traditional media, such as television and newspapers, are frequently the subject of crime-relationship research, they have grown increasingly irrelevant. As traditional media declines \cite{rnielsen}, social media, such as Twitter, Facebook, and Reddit, has risen in its place. Due to this shift in media consumption patterns, an increasing number of people receive news through social media \cite{hkwak}, including stories that focus on crime. However, social media faces some challenges not found in the traditional media landscape. Due to the free and open nature of who can post on social media, submissions containing misinformation \cite{kognyanova} and manipulation of content \cite{aarif} have remained a challenge for social media companies to reign in.

\par As social media begins to fill traditional media's niche, one might wonder how the landscape of crime reporting and discussion might change. In this work, we analyze the discussion of crime on the social media website Reddit. Specifically, we examine how crime discussion takes shape on 384 unique communities in the United States. To measure crime discussion, we have developed a Reddit crawler to fetch submitted posts from the 384 selected communities. We then utilize textual analysis techniques to identify posts that discuss crime while minimizing false positives. We analyze the data collected by the crawler to determine a community's level of crime discussion in comparison to its population, voting patterns, and documented crime rate. Lastly, we dive into the posting histories of users who post to Reddit's New York City community to identify any further trends or patterns.

@@

\subsection{Scope}

\par Before we begin the gathering of the data, we must first understand the scale at which the data should be collected. First, we are collecting data that pertains to the United States. Much research has focused on the relationship between crime and media specifically within the United States. The United States Census Bureau also provides plentiful contextual and reference data. Second, in a general sense, we want to measure at a city-level scale. The city is the base-level at which a critical mass of population can support an online community; a city provides a geographic center and a name to associate with a community. However, the definition of a city is rather murky. The definition varies on a state-by-state basis due to the nature in which a state delineates county-level subdivisions. All states are broken down into counties, but differ in how counties are partitioned. For example, New York breaks down counties into towns and cities, while North Dakota only subdivides counties into cities, with excluded areas remaining unincorporated. In this way, we can think of city limits and city populations as somewhat arbitrary. There is no consistent, uniform definition, so one should be careful when comparing cities for analysis purposes.

@@

\par To best equalize differences in city definitions, we use statistical area delineations provided by the United States Census Bureau to normalize city population and sizes. The first and most precise definition is of Urban Areas (UAs) and Urban Clusters (UCs). UAs are dense clusters of people that house over 50,000 people. UCs are similarly measured dense clusters of people with between 2,500 and 50,000 residents. UAs and UCs are computed by first identifying a dense cluster of census blocks, the smallest census geography. From here, the UA or UC snakes off from the central core to include housing that fits the density requirements in less dense census blocks \cite{censusurban}. This process creates the ``true'' city limits, which are unaffected by municipal boundaries.

@@

\par When analyzing our selected Reddit communities, we need to consider the geospatial aspects of social media. In some sites, specific geographic location is intrinsic to the functionality of the product, whereas in others, anyone can browse a community for somewhere far away. For example, on Reddit there is no barrier preventing someone from, for example, Los Angeles from posting in a New York City community. Scellato et al. \cite{sscellato} measure the geographic nature of social networks through the comparison of geospatial proximity of graph-connected users on four social media sites. They found that sites, such as FourSquare, that had an explicitly geographic nature produced a higher degree of locality. However, sites that focused more on general information exchanges, such as Twitter, showed less geographic clustering.

\par The Reddit communities we analyze hold an interesting space between these two categories; they are both tied to place and detached from it. There is no geographic component stopping a user from posting to a distant community, but the geospatial nature of the community itself can lead to geographic clustering. In this way, we must determine if those posting in a certain community are truly local.

@@

\par An increase in fear of crime can have implications beyond elevated negative emotions. Fear of crime has far-reaching social\cite{lheath}, political \cite{yjewkes}, and institutional \cite{vsacco} impacts. Belief in excessive amounts of crime can lead to loss of community cohesion; Heath and Gilbert found that as television news media consumption increased, distrust both in the local community and the world ``out there'' increased \cite{lheath}. Additionally, media creators often sensationalized stories, turning unfortunate incidents into grim spectacles. Those that perceived crime to be worse than others were more likely to perform excessive crime prevention actions, such as not leaving their house or engaging with the neighborhood.

\par Liu et al. \cite{jliu} describe how the prevalence of crime discussion affected the 2016 presidential election in the United States. The authors found that voters who consumed more television in turn consumed more campaign advertisements. About 15\% of campaign advertisements covered issues such as crime and violence. Frequent crime media consumers assumed crime and violence issues to be worse than they really are \cite{jshanahan}. Furthermore, the authors found that excessive crime reporting and media exposure had impacts on voting patterns; those that believed crime to be worse tended to vote for more conservative candidates.

\par Worry of crime victimization can lead to the creation of institutional policies meant to combat the perceived threat. One notable example is the idea of Broken Windows Theory \cite{jwilson} and a practice that stemmed from its development, known as stop and frisk \cite{tmeares}. Broken Windows Theory states that visible signs of crime and disorder lead to further crimes and disorder \cite{jwilson}. Essentially, the theory states that ignoring minor criminal incidents can lead to more frequent and serious issues. Acting on this theory, the New York Police Department instituted a stop and frisk policy, in which police officers temporarily detained civilians suspected of carrying illegal objects \cite{tmeares}. The policy, while believed to be effective at the time, has since come under scrutiny. Researchers found that only 6\% of stops resulted in arrests \cite{tmeares} and that there is no clear proof that stop and frisk contributed to the decline in crime in New York City \cite{dweisburd}. Stop and frisk was removed as a policy in 2013 when it was deemed unconstitutional \cite{tmeares}.

@@

\par While the relationship between traditional media and crime has been thoroughly researched, the relationship between social media and crime has not been as rigorously explored. Social media has grown and evolved beyond its humble beginnings. Social media sites, such as Twitter, are now the main source of news for many Americans \cite{hkwak}. Walker and Masta found that nearly half of Americans consume their news from social media sites like Twitter, Facebook, and Reddit \cite{pewresearch}. This trend coincides with the decline of traditional media. Printed media, such as newspapers and magazines, as well as televised media, have consistently declined since the explosive growth of the Internet \cite{rnielsen}.

Curiel et al. \cite{curiel} detail the ecosystem of crime discussion on Twitter. Specifically, they look at how often crime discussion appears in Tweets posted from users in Latin American countries. Using Twitter's geolocation tags, Tweets are subdivided down to the municipality that the original user posted from. From here, the authors compared Twitter crime discussion rates to city-level documented crime rates. They did not find a correlation between high frequencies of crime-related Tweets and high rates of reported crime. The authors conclude that the Tweets do not accurately represent actual rates of crime, but they effectively capture the worry of crime in a community.

The authors introduce an interesting observation: some of the crime-related Tweets are highly sensationalized postings from a group of ``involved users'' that frequently comment about violence \cite{curiel}. In this way, social media differs from traditional media. Traditional media acts as a gatekeeper, where only select stories and viewpoints emerge and factchecking generally exists in mainstream publications \cite{vsacco}. Social media, on the other hand, allows for a more diverse set of viewpoints and opinions. However, as moderation policies vary \cite{szannettou} on social media platforms, blatantly false stories can spread across sites if left unchecked. This proliferation of misinformation has become increasingly impactful in the United States. It has affected important events in recent American history, including presidential elections \cite{jliu} and the the response to the Covid-19 pandemic \cite{amian} \cite{ftahmsabi}. Without intervention, falsehoods and panics continue to spread across the web.

@@

\subsection{Reddit Data}
\par The Reddit dataset contains posts from the subreddits of the principal cities of the 384 MSAs of the United States as of March 2020 \cite{censusmetro}. From this list of subreddits, we fetch and store all posts that users submit. In total, 161,166 posts were gathered between April 5, 2022 and May 31, 2022. A timeline of this process can be seen in Figure \ref{fig:line-1}. The datastore archives posts in two formats. First, posts are written to a system of record to ensure that there is an authoritative data source that can be referenced. Second, pertinent information, such as post title and author, is extracted from the posts data stream and placed in a separate datastore.

@@

\par After storing data, an analysis tool runs to determine if a post is about crime. To do this, a regular expression checks if a post's title or a post's link's URL contains a crime-related keyword. These keywords were derived from actions that constitute violent crime and their synonyms, as well as generic crime-related words. In total, 124 crime-related keywords are used. If the regular expression returns a hit, a flag is raised in the database denoting that the post is about crime. Overall, 6,792 of the collected posts are estimated to discuss crime.

\par Due to the nature of text analysis, a number of false positives might be considered, while some false negatives go undetected. False negatives can be hard to detect, as they include dog-whistles, local-dependent terms, and ambiguous references \cite{curiel}. Certain posters may choose to keep their posts ambiguous so as to keep their intentions visible to only a small group \cite{aaddawood}. To determine the rate of false positives, we analyze a sample of stored posts. We look for phrases such as ``I shot a picture'' that do not relate to crime, but contain a crime-related keyword. Of a sample of 400 posts, we find that 36 posts do not relate to crime, for an accuracy rate of 91\%. Similar analysis done on the social media site Twitter reached a rate of 66\% accuracy \cite{curiel}.

\subsection{Contextual Data}
\par We utilize a variety of data to highlight trends in the Reddit posts. One variable that subreddits are compared to is population size of the MSA. These values range from a minimum of 58,639 (Carson City, NV) and a maximum of 20,140,470 (New York-Newark-Jersey City, NY-NJ-PA). MSAs are categorized into four bins based on their size: large, medium, small, and very small. The population cutoffs are 1,000,000, 500,000, and 200,000. The large population bin contains 56 members, the medium bin contains 54 members, the small bin contains 113 members, and the very small bin contains 161 members.

\par Another variable that provides context is the political climate of an MSA. For this metric, we consider the results of the 2020 election \cite{ap} in terms of the percent of the MSA voting Democrat. In this case, we only document Democrat and Republican votes. These values range from a minimum of 20.2\% (Morristown, TN) to a maximum of 80.9\% (Santa Cruz-Watsonville, CA). The MSAs are categorized into five bins based on their voting results: Very Conservative, Conservative, Moderate, Liberal, and Very Liberal. The percentage cutoffs for the bins are 37.5\%, 47.5\%, 52.5\%, and 62.5\%. The Very Conservative bin contains 112 members, the Conservative bin contains 103 members, the Moderate bin contains 57 members, the Liberal bin contains 73 members, and the Very Liberal bin contains 39 members.

\par A third variable that is considered is the documented violent crime rate of each MSA. This data is derived from the FBI's Uniform Crime Reporting \cite{ucr} statistics. \footnote{Data from the FBI mostly comes from the year that is most recent, 2019. However, not all municipalities report information, so there are slight estimations in the data \cite{ucr2}} Documented violent crime rates range from a minimum of 44.3/100,000 (Bangor, ME) to a maximum of 1,397.2/100,000 (Birmingham-Hoover, AL). We select violent crime rates for our comparison data because they are less ambiguous than property crimes. For example, police departments are less likely to differ in their definition of a homicide compared to criminal mischief. Additionally, documented crime data is normalized using the min-max normalization method. This method condenses all values in a range between a value of 0 and 1, where 1 is the highest value in the range and 0 is the lowest. In doing so, we can compare crime data to a similarly normalized crime discussion value from the Reddit data.

\section{Methods}
\par We use one main crawler to gather post data from Reddit. This crawler utilizes multiple different tools to gather disparate pieces of data and place them into two datastores. The crawler checks for new posts once every hour so that posts can be fetched before a user deletes them or a moderator removes them. These communities are generally slow moving, with an average of 111 posts an hour between all 384 subreddits.

\par To gather the data, the crawler first sends requests to the Reddit REST API \cite{reddit}. We use the \texttt{new} endpoint for each subreddit to check the most recent posts. The post last written to the database for each subreddit is cached in a database table so that we can take advantage of the \texttt{after} parameter of the API. This parameter allows us to take posts that have been created since a given post ID. The \texttt{after} parameter is especially useful on slower subreddits; without it, we would be fetching posts that might be months old. If the cached value does not exist or is not valid, then the most recent hundred posts are gathered. This is the maximum allowable value by the Reddit API.

\par After performing error checking to ensure all of our requests went through, each record is sent to two databases. The first is a CockroachDB database that acts as a system of record. Raw posts are stored here in a simple format: \texttt{id}, \texttt{timestamp}, and \texttt{data}, the last of which is the data retrieved from the Reddit API in JSON format. After writing to CockroachDB, the crawler then writes the JSON data from Reddit to ElasticSearch. ElasticSearch provides quick and efficient text analysis that allows for the extraction of certain keywords in post titles and URLs.

\par The crawler and databases run in Docker containers. Containerization allows the tool, as well as the databases, to run in a clean, isolated environment without worrying about being choked out by other processes. Additionally, the crawler-container is scheduled by Kubernetes to allow for a higher degree of availability and resilience. If something unexpected occurs and the tool goes down, it will simply be restarted by Kubernetes.

@@

\par In total, the Reddit crawler gathered 161,166 posts between 384 subreddits. Posts were collected between April 5th, 2022 and May 31, 2022. Table \ref{table:table-1} details the ten most active subreddits of those monitored. Similarly, Table \ref{table:table-2} lists the ten most active subreddits when normalized by population.

@@

\par Furthermore, Figure \ref{fig:map-1} displays a map of all Metropolitan Areas by the percentage of crime posts submitted to their respective subreddits. The darker the shade of green, the more posts discuss crime. The average crime discussion percentage is 3.5\%.

@@

\par From Figure \ref{fig:graph-1}, we can see that as population increases, documented crime rates gradually increase. This trend is reflected in the crime discussion data. Crime discussion scores are roughly equivalent for the very small, small, and medium buckets. However, the large population bucket has a much higher crime discussion score than that of the other buckets. The large population bucket has a 6\% greater score than the medium population bucket when comparing documented crime data, but the large population bucket has a 56\% greater score than the medium population bucket when comparing crime discussion data.

\par Figure \ref{fig:cdf-1} shows a cumulative distribution function of the data by population bucket. Here, we can see that the members of the large population bucket have higher crime discussion scores. When looking at the very small MSAs, we notice quite a few outliers. We can see that some Metropolitan Areas in this category have among the highest amounts of crime discussion. However, almost 20\% of very small MSA subreddits have not discussed crime at all. The small bucket has the next highest percentage of subreddits with zero crime discussion, with about 8\% of communities not discussing crime at all.

@@

\par Another factor to consider alongside crime discussion is the reported crime rate of an MSA. Higher documented crime rates can lead to increased amounts of crime discussion, as crime may affect more members of the community. To measure MSA crime rates, we use the FBI's Uniform Crime Reporting Estimates \cite{ucr}. The 384 Metropolitan Areas represent a differing level of crime rates, with a high of 1,397.2 from Birmingham-Hoover, AL, a low of 44.3 from Bangor, ME, and an average of 380.9 among all MSAs. Table \ref{table:table-3} displays the MSAs with the ten highest documented crime rates. In this case, crime rates are defined as the amount of violent crime per 100,000 people. Additionally, the map in Figure \ref{fig:map-3} displays the crime rate for all Metropolitan Areas.

\begin{table}[h!]
    \centering
    \small
    \caption{MSAs with highest crime rates}
    %\begin{tabu} to 1.0\textwidth {| *{3}{c|} }
    \begin{tabular}{| c | r | r |}
    \hline
    Metropolitan Statistical Area & Crime Rate & \% Crime Discussion\\ \hline
    Birmingham-Hoover, AL & 1,397.2 & 2.52 \\ \hline
    Farmington, NM & 1,199.8 & 1.61 \\ \hline
    Anchorage, AK & 1,194.6 & 2.36 \\ \hline
    Kansas City, MO-KS & 1,159.4 & 3.16 \\ \hline
    Memphis, TN-MS-AR & 1,120.5 & 3.43 \\ \hline
    Winston-Salem, NC & 1,073.6 & 2.32 \\ \hline
    Albuquerque, NM & 1,043.4 & 4.53 \\ \hline
    Danville, IL & 935.7 & 0.00 \\ \hline
    Pine Bluff, AR & 895.4 & 12.5 \\ \hline
    Odessa, TX & 881.8 & 4.30 \\ \hline
	\end{tabular}
	\label{table:table-4}
\end{table}

@@

\par From the data collected by our Reddit crawler, we have seen that crime discussion is widespread among the selected communities. However, while we have analyzed posts about crime, we have not yet analyzed the users that initiate this crime discussion. In doing so, we can potentially identify trends in the data that could highlight motivations behind crime posters or their submission patterns. We can also attempt to identify if crime posters are truly local by seeing if they overlap with other state and local subreddits.

@@

\par We have discussed the nature and prevalence of crime discussion on Reddit, a social media website, as it pertains to location-based communities. To obtain the necessary data and information, we have created a highly resilient Reddit crawler that fetches all posts from communities that represent the 384 Metropolitan Statistical Areas of the United States. The crawler gathered 161,166 posts over a two-month time span. Of these 161,166 posts, a total of 6,792 were determined to discuss crime.
